% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2007-2010 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\definecolor{mygrey}{gray}{0.80}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{\large{Radu Creanga}}  & 814-218-7238 \\
487 Jackson Park Drive &  rdcrng@gmail.com \\
Meadville, PA 16335 & http://sites.google.com/site/rdcrng \\
\end{tabular*}
\\

\vspace{0.1in}

\resheading{Education}
\begin{itemize}
\item
	\ressubheading{Allegheny College}{Meadville, PA}{Bachelor of Science in Computer Science}{Sep. 2007 - May 2011}
	\begin{itemize}
		\resitem{Senior Comprehensive Project: Implicit Load Balancing for the Linux Scheduler}
	\end{itemize}
\end{itemize}

\resheading{Work Experience}
\begin{itemize}
\item
	\ressubheading{Department of Computer Science}{Allegheny College}{Research Assistant}{May 2008 - Present}
	\begin{itemize}
	    \resitem{Under the supervision of Dr. Gregory M. Kapfhammer I am extending my senior comprehensive projectwith the goal to demonstrate the viability of Implicit Load Balancing at improving the Linux scheduler's scalability across an increasing number of CPUs (http://github.com/rdcrng/LinSchedSim).}
		\resitem{Under the supervision of Dr. Matthew C. Jadud I implemented Pulse Width Modulation functionality for the Plumbing library (http://concurrency.cc/book/).}
		\resitem{Under the supervision of Dr. Robert D. Cupper I redesigned and implemented XInteract - classroom software currently being used at Allegheny College that allows instructors to teach introductory programming courses using a more tailored and focused approach.}
		\resitem{Under the supervision of Dr. Robert S. Roos I explored an ant colony optimization technique based on Lindenmayer systems.}
	\end{itemize}
	
\item
	\ressubheading{Learning Commons}{Allegheny College}{Technology Consultant}{Jan. 2008 - May 2011, Academic Months}
	\begin{itemize}
		\resitem{Trained Allegheny students to use software in their academic pursuits, including document editing, basic website creation, movie and photo editing, and blogging software usage.}
		\resitem{Held incoming student technology orientation workshops.}
	\end{itemize}

\item
	\ressubheading{Department of Computer Science}{Allegheny College}{Teaching Assistant}{Sep. 2009 - Dec. 2010}
	\begin{itemize}
		\resitem{Attended weekly recitation sessions during which I answered questions related to the assignment of that week.}
		\resitem{Held office hours during which I was available to all the students in the class for questions related to the course.}
		\resitem{Periodically helped the instructor of the course with grading laboratory assignments.}
	\end{itemize}

\item
	\ressubheading{Learning Commons}{Allegheny College}{Computer Science Tutor}{Sep. 2009 - May 2010}
	\begin{itemize}
		\resitem{Assisted student in correctly understanding the course material.}
		\resitem{Used alternative (non-code) examples to help them complete lab assignments.}
	\end{itemize}
	
\end{itemize}

\pagebreak

\resheading{Skills}

\begin{description}
\item[Spoken Languages:]
Fluent in English, Romanian, and Russian.
\item[Programming Languages:]
C/C++, Fortran, Java, Python, R, C\#, BASH, SQL, Scheme, Occam-$\pi$.
\item[Operating Systems:]
Windows XP / 7, Linux (Fedora / Ubuntu)
\item[Tools / Technologies:]
Java Swing, JavaBeans, Object Relational Mapping (Cayenne, Hibernate, JPA, EclipseLink, TopLink), JDBC, Database Software (Apache Derby, Java DB, SQL Server, SQLite, MySQL), SimPy, Python NetWorkSpaces, Git, Subversion, \LaTeX{}.
\item[Miscellaneous:]
Like to discover new technologies and excel at adapting existing tools to my development needs.
\end{description}

\resheading{Extracurricular Activities}
\begin{itemize}
\item
	\ressubheading{Student Chapter of the Association for Computing Machinery}{Allegheny College}{President}{Sep. 2010 - May 2011}
\item
	\ressubheading{International Club}{Allegheny College}{President}{Sep. 2010 - May 2011}
\item
	\ressubheading{Student Chapter of the Association for Computing Machinery}{Allegheny College}{Vice-President}{Sep. 2009 - May 2010}
\item
	\ressubheading{International Club}{Allegheny College}{Vice-President}{Sep. 2009 - May 2010}
\item
	\ressubheading{International Club}{Allegheny College}{Treasurer}{Sep. 2008 - May 2009}
\end{itemize}

\resheading{References}
\begin{itemize}
\item
	\ressubheading{Mathew C. Jadud}{mathew.jadud@allegheny.edu}{Professor and Academic Advisor}{http://www.jadud.com/MCJ.html}
\item
	\ressubheading{Gregory M. Kapfhammer}{gkapfham@allegheny.edu}{Professor and Senior Comprehensive Project Advisor}{http://www.cs.allegheny.edu/sites/gkapfham/}
\item
	\ressubheading{Robert D. Cupper}{bcupper@allegheny.edu}{Professor}{http://www.cs.allegheny.edu/sites/bcupper/}
\item
	\ressubheading{Robert S. Roos}{rroos@allegheny.edu}{Professor}{http://www.cs.allegheny.edu/sites/rroos}
\item
	\ressubheading{Helen McCullough}{hmccull@allegheny.edu}{Supervisor at the Learning Commons}{http://webpub.allegheny.edu/employee/h/hmccull/}
\end{itemize}


\end{document}
